### 2014-03-09 etc/abstract.tex
update
udpate

% 1.Statetheproblem
Mutation analysis is a metric for measuring the quality of test suites. However, its exorbitant computational requirements makes it hard to use in practice. Choosing a smaller subset of mutations to run is a simple approach that can alleviate this problem. There exist multiple ways to reduce the set of mutations to run. Operator selection has recently been in the focus. However recently researchers have found that sampling can achive accuracy and mutant reduction similar to operator selection.

@@

%4.Saywhatfollowsfromyoursolution
Our experiments rank sampling criterias that can be used by testers according how much mutant reduction is achieved, their ability to predict the final mutation score, the relative effect of unit increase in sampled mutation score on the final score, and also the time required for the run.

>>>>

% 1.Statetheproblem
Mutation analysis is a metric for measuring the quality of test suites. However, it is computationally intensive compared to other measures which it hard to use in practice. Choosing a smaller subset of mutations to run is a simple approach that can alleviate this problem. There exist multiple ways to reduce the set of mutations to run. Operator selection has recently been in the focus. However recently researchers have found that sampling can achive accuracy and mutant reduction similar to operator selection.

@@

%4.Saywhatfollowsfromyoursolution
Our experiments rank sampling criterias that can be used by testers according how much mutant reduction is achieved, their ability to predict the final mutation score, the relative effect of unit increase in sampled mutation score on the final score, and also the time required for the run. We also find that sampling techniques work better than operator selection methods including statement deletion in both mutation reduction and accuracy of approximation to the full mutation score.

### 2014-03-09 src/analysis.Rnw
udpate

o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
colnames(o.stats.sel.xp) <- new.colnames
colnames(r.stats.sel.xp) <- new.colnames
@

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.xp, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.xp, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The x\% random selection criteria results.}
\label{tbl:xsel}
\end{table*}

\begin{figure*}[t]
<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#myopts <- theme(panel.background = element_blank())
#myopts <-   theme_bw() +
#  opts(axis.line = theme_segment(colour = "black"),
#    panel.grid.major = theme_blank(),
#    panel.grid.minor = theme_blank(),
#    panel.border = theme_blank(),
#    panel.background = theme_blank()) 
  #theme with white background
myopts <- theme_bw() +
  #eliminates background, gridlines, and chart border
  theme(
    plot.background = element_blank()
   ,panel.grid.major = element_blank()
   ,panel.grid.minor = element_blank()
   ,panel.border = element_blank()
  ) + 
  #draws x and y axis line
  theme(axis.line = element_line(color = 'black'))
myopts <-  theme_classic() 
#+ opts(strip.background = theme_rect(colour = 'NA', fill = 'NA')) + opts(strip.text.y = theme_text(colour = 'white')) + theme(axis.line = element_line(color = 'black'))

o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts
@
\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\label{fig:xsamplesel}
\end{figure*}
%TODO : See if the following paragraph is needed, or shall we just sink the ceil(x) discussion completely?
Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.

@@

\subsection{Operator Selection}
<<opsel>>=
stats.op <- subset(stats.rest, grepl('^(op|TSDL)', operator))
o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^(op|TSDL)', operator))
colnames(o.stats.sel.op) <- new.colnames
colnames(r.stats.sel.op) <- new.colnames
@

>>>>

o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
colnames(o.stats.sel.xp) <- new.colnames
colnames(r.stats.sel.xp) <- new.colnames
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(subset(o.stats.sel.xp, grepl('^r[.]', operator)), caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(subset(r.stats.sel.xp, grepl('^r[.]', operator)), caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The round(x)\% random selection criteria results.}
\label{tbl:xsel}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(subset(o.stats.sel.xp, grepl('^rr[.]', operator)), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(subset(r.stats.sel.xp, grepl('^rr[.]', operator)), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results.}
\label{tbl:xsel2}
\end{table*}

\begin{figure*}[t]
<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
theme_set(theme_bw(12))
myopts <- theme(panel.background = element_blank())
#myopts <-   theme_bw() +
#  opts(axis.line = theme_segment(colour = "black"),
#    panel.grid.major = theme_blank(),
#    panel.grid.minor = theme_blank(),
#    panel.border = theme_blank(),
#    panel.background = theme_blank())
  #theme with white background
#myopts <- theme_bw() +
  #eliminates background, gridlines, and chart border
#  theme(
#    plot.background = element_blank()
#   ,panel.grid.major = element_blank()
#   ,panel.grid.minor = element_blank()
#   ,panel.border = element_blank()
#  ) +
  #draws x and y axis line
#  theme(axis.line = element_line(color = 'black'))
#myopts <-  opts() #theme_classic()
#+ opts(strip.background = theme_rect(colour = 'NA', fill = 'NA')) + opts(strip.text.y = theme_text(colour = 'white')) + theme(axis.line = element_line(color = 'black'))

# TODO - replace by o.processed.
o.xp <- subset(r.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts
@
\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(r.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of sample(x) reduction(randoop). All are above 0.90 $R^2$.}
\label{fig:xsamplesel}
\end{figure*}
%TODO : See if the following paragraph is needed, or shall we just sink the ceil(x) discussion completely?
Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.

@@

\subsection{Operator Selection}
\begin{figure*}[t]
<<op.all,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
df$sqr <- 1 - df$r.square
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              NA)))))))
df$strat <- with(df,
    ifelse(grepl('perunit', strategy), 'xpercent',
      ifelse(grepl('op',strategy), 'opsel',
        ifelse(grepl('one',strategy), 'oneperelm',
          ifelse(grepl('elem',strategy), 'loc', 'other'
            )))))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
@
\end{figure*}
\begin{figure*}[t]
<<op.all.2,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
@
\end{figure*}
\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
dfd <- subset(df, !(strategy %in% c('op','opsel')) )
ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
@
\end{figure*}
<<opsel>>=
stats.op <- subset(stats.rest, grepl('^(op|TSDL)', operator))
o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^(op|TSDL)', operator))
colnames(o.stats.sel.op) <- new.colnames
colnames(r.stats.sel.op) <- new.colnames
@
